Measuring contrast processing in the visual system using SSVEP

### 2024-04-13 review.qmd
Fixed fig captions

```{python}
#| label: fig-centresurround
#| fig-cap: The perceived contrast of a stimulus depends on its context. A high contrast surround reduces the apparent contrast of the central 'probe' region
#| fig-cap-location: bottom

@@

```{python}
#| label: fig-plotsinewaves
#| fig-cap: a) A typical SSVEP setup: a screen, a grating, a flicker rate: b) The responses from a single electrode (time domain) c) Frequency domain.
#| fig-cap-location: bottom

@@

```{python}
#| label: fig-plotspectra
#| fig-cap: Temporal frequency representations of combining two inputs at frequencies F1=5Hz and F2=7Hz. A pure sine-wave input would generate responses only at F1 and F2. However, the rectification that accompanies early visual processing converts this contrast reversal into a more complex frequency-domain representation with power predominantly at the second harmonics 2F1 and 2F2.
#| fig-cap-location: bottom

@@

```{python}
#| label: fig-contrastresponsefunction
#| fig-cap: Non-linear contrast response function resulting from the population average of two full-wave rectified signals passing through a non-linear transducer. Note the 'supersaturation' at high contrast levels.
#| fig-cap-location: bottom

@@

```{python}
#| label: fig-intermodulation
#| fig-cap: Non-linear combination of two independent contrast modulations at F1 and F2 results in 'intermodulation' terms that appear at low-order sums and differences of those frequencies
#| fig-cap-location: bottom

@@

#| label: fig-sweepvep
#| fig-cap: Sweep VEP simulation showing how a contrast detection threshold can be estimated from sweep VEP data measured at higher contrasts.
#| fig-cap-location: bottom

@@

```{python}
#| label: fig-plotclinical
#| fig-cap: Example contrast response functions for different clinical conditions. Panel (a) shows modelled contrast response functions for epilepsy patients (blue) and control participants (black), based on the data of Tsai et al. (2011). Panel (b) shows functions for the amblyopic (red) and fellow (black) eyes of adults with amblyopia, based on the data of Baker et al. (2015). Panel (c) shows functions for children with (green) and without (black) a diagnosis of autism, based on the data of Vilidaite et al. (2018). Panel (d) shows data from *Drosophila melanogaster* (fruit flies) in Afsari et al 2014. One day-old flies expressing a human gene linked to Parkinson's (hLRRK-G2019S) show increased SSVEP response amplitude and sensitivity compared to control animals.
#| fig-cap-location: bottom

>>>>

```{python}
#| label: fig-centresurround
#| fig-cap: "The perceived contrast of a stimulus depends on its context. A high contrast surround reduces the apparent contrast of the central 'probe' region."
#| fig-cap-location: bottom

@@

```{python}
#| label: fig-plotsinewaves
#| fig-cap: "a) A typical SSVEP setup: a screen, a grating, a flicker rate: b) The responses from a single electrode (time domain) c) Frequency domain."
#| fig-cap-location: bottom

@@

```{python}
#| label: fig-plotspectra
#| fig-cap: "Temporal frequency representations of combining two inputs at frequencies F1=5Hz and F2=7Hz. A pure sine-wave input would generate responses only at F1 and F2. However, the rectification that accompanies early visual processing converts this contrast reversal into a more complex frequency-domain representation with power predominantly at the second harmonics 2F1 and 2F2."
#| fig-cap-location: bottom

@@

```{python}
#| label: fig-contrastresponsefunction
#| fig-cap: "Non-linear contrast response function resulting from the population average of two full-wave rectified signals passing through a non-linear transducer. Note the 'supersaturation' at high contrast levels."
#| fig-cap-location: bottom

@@

```{python}
#| label: fig-intermodulation
#| fig-cap: "Non-linear combination of two independent contrast modulations at F1 and F2 results in 'intermodulation' terms that appear at low-order sums and differences of those frequencies."
#| fig-cap-location: bottom

@@

#| label: fig-sweepvep
#| fig-cap: "Sweep VEP simulation showing how a contrast detection threshold can be estimated from sweep VEP data measured at higher contrasts."
#| fig-cap-location: bottom

@@

```{python}
#| label: fig-plotclinical
#| fig-cap: "Example contrast response functions for different clinical conditions. Panel (a) shows modelled contrast response functions for epilepsy patients (blue) and control participants (black), based on the data of Tsai et al. (2011). Panel (b) shows functions for the amblyopic (red) and fellow (black) eyes of adults with amblyopia, based on the data of Baker et al. (2015). Panel (c) shows functions for children with (green) and without (black) a diagnosis of autism, based on the data of Vilidaite et al. (2018). Panel (d) shows data from *Drosophila melanogaster* (fruit flies) in Afsari et al 2014. One day-old flies expressing a human gene linked to Parkinson's (hLRRK-G2019S) show increased SSVEP response amplitude and sensitivity compared to control animals."
#| fig-cap-location: bottom
